---
title: "hw_emperical"
author: "LonghaoChen"
date: "3/4/2019"
output: 
  pdf_document: 
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Is the data in the file maybe uniform.txt distributed as a Uniform distribution on [0, 1]?
```{r}
library(reshape2)
library(tidyverse)
library(fitdistrplus)
library(car)
maybe_uniform <- read.table("~/Desktop/MA677/HW/maybe_uniform.txt", quote="\"", comment.char="")
maybe <- reshape2::melt(maybe_uniform)
qqPlot(maybe$value,distribution = "unif")
plotdist(maybe$value, demp = TRUE)
descdist(maybe$value, obs.col = "red",boot=1000)

```

Yes, I believe it is close to uniform distribution.

Is it possible that the model below is better than the Uniform?



Is there a third model that is a better fit?
Not really from our plot.

2. Is the data in the file maybe normal.txt a random sample from the
normal distribution with mean = 26 and variance = 4? Investigate
your result. Make a qnorm plot. Make a histogram. Be ready to show
and discuss your results.

```{r}
maybe_normal <- read.table("~/Desktop/MA677/HW/maybe_normal.txt", quote="\"", comment.char="")
normal <- reshape2::melt(maybe_normal)
qqPlot(normal$value,distribution = "unif")
plotdist(normal$value, demp = TRUE)
descdist(normal$value, obs.col = "red",boot=1000)
fit <- fitdistr(normal$value, densfun="normal") 
fit
```

I think it is close to a normal distribution with mean at 26 and variance at 4, since I have evidence from qqplot, histrogram and from fitdistr function.

3. Are the two samples in X, maybe same 1.txt, and Y , maybe same 2.txt,
from the same distribution? Could it be that X + 2 and Y have the
same distribution?

```{r}
maybe_same1 <- read_table2("~/Desktop/MA677/HW/maybe_same_1.txt", 
    col_names = FALSE, col_types = cols(X1 = col_number(), 
        X2 = col_number(), X3 = col_number(), 
        X4 = col_number(), X5 = col_number()))
maybe_same2 <- read_table2("~/Desktop/MA677/HW/maybe_same_2.txt", 
    col_names = FALSE, col_types = cols(X1 = col_number(), 
        X2 = col_number(), X3 = col_number(), 
        X4 = col_number(), X5 = col_number()))

same1 <- reshape2::melt(maybe_same1,id.vars=NULL)
same2 <- reshape2::melt(maybe_same2,id.vars=NULL)

qqPlot(same1$value,distribution = "unif")
plotdist(same1$value, demp = TRUE)
descdist(same1$value, obs.col = "red",boot=1000)

qqPlot(same2$value,distribution = "unif")
plotdist(same2$value, demp = TRUE)
descdist(same2$value, obs.col = "red",boot=1000)

qqPlot(same2$value+2,distribution = "unif")
plotdist(same2$value+2, demp = TRUE)
descdist(same2$value+2, obs.col = "red",boot=1000)
```
By comparing the plots of X, Y and X+2, I think the the relationship is stronger between X and Y rather than X+2 and Y. Therefore, X and Y are more likely to come from the same distribution.

4. Read the data in the file norm data.Rdata. There are 25 data points.
Is this a data set drawn from the **standard normal distribution**
Use ecdf() to compute the empirical distribution of the data. Create
a normal distribution that can be used to calculate the KolmogorovSmirnov test. Calculate the D statistic. Run the ks.test() function
and compare your results to the results reported by ks.test.

```{r}
mydata <- readRDS("~/Desktop/MA677/HW/norm_sample.Rdata")
b <- ecdf(mydata)
plot(b)
a <- rnorm(n = 25,mean = 0,sd = 1)
ks.test(x = mydata,y = a)
```
Our results indicate that the data is not standard normal distribution.

5. Produce empirical distributions with confidence bands for the fujiquakes.dat and faithful.dat. For the fujiquakes data, Find a 95for
F(4.9) − F(4.3). For the faithful data, estimate a 90 percent confidence interval for the mean waiting time and estimate the median
waiting time.

